### 2023-04-16 my_paper/tables/tab04-summary-stats.tex
some edits

\begin{table}[!h]

@@

Variables & \specialcell{White Father \\ White Mother \\ (WW) \\ (i)} & \specialcell{White Father \\ Hispanic Mother \\ (WH) \\ (ii)} & \specialcell{Hispanic Father \\ White Mother \\ (HW) \\ (iii)} & \specialcell{Hispanic Father \\ Hispanic Mother \\ (HH) \\ (iv)} & \specialcell{HH - WW \\ (v)} & \specialcell{HW - WH \\ (vi)}\\

@@

\textbf{Panel A: Parent’s} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\

@@

\textbf{Panel C: Employment and Earnings} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\

@@

\hspace{1em}Women’s Hourly Earnings & \specialcell{2.26\\(0.43)} & \specialcell{2.32\\(0.45)} & \specialcell{2.27\\(0.45)} & \specialcell{2.3\\(0.41)} & \specialcell{0.04***\\(0.01)} & \specialcell{-0.05**\\(0.02)}\\

@@

\hspace{1em}Women’s Hourly Earnings & \specialcell{9.44\\(1.59)} & \specialcell{9.55\\(1.59)} & \specialcell{9.47\\(1.55)} & \specialcell{9.52\\(1.52)} & \specialcell{0.08**\\(0.02)} & \specialcell{-0.08*\\(0.05)}\\

@@

\item[1] The data is restricted to native-born United States citizens between 1994 and 2019 who are also White and between the ages of 25 and 40. I identify the ethnicity of a person's parents through the parent's place of birth. A parent is Hispanic if they were born in a Spanish-speaking country. A parent is White if they were born in the United States.
\item[2] In each column, I present the average statistics of the different types of people based on the ethnicities of their parents. In column one, I show the summary statistics of children of White fathers and White mothers. In column two, I present the summary statistics of children of White fathers and Hispanic mothers. In column three, I show the summary statistics of children of Hispanic fathers and White mothers. In column four, I present the summary statistics of children of Hispanic fathers and mothers.
\item[3] Columns five and six have data on the HH--WW gaps (column five) and the HW--WH gaps (column six).

>>>>

\begin{table}[H]

@@

Variables & \specialcell{White Father \\ White Mother \\ (WW) \\ (1)} & \specialcell{White Father \\ Hispanic Mother \\ (WH) \\ (2)} & \specialcell{Hispanic Father \\ White Mother \\ (HW) \\ (3)} & \specialcell{Hispanic Father \\ Hispanic Mother \\ (HH) \\ (4)} & \specialcell{HH - WW \\ (5)} & \specialcell{HW - WH \\ (6)}\\

@@

\textbf{Panel A: Children's Sunthetic Parent} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\

@@

\textbf{Panel C: Children's Employment and Earnings} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\

@@

\hspace{1em}Women’s Log Hourly Earnings & \specialcell{2.26\\(0.43)} & \specialcell{2.32\\(0.45)} & \specialcell{2.27\\(0.45)} & \specialcell{2.3\\(0.41)} & \specialcell{0.04***\\(0.01)} & \specialcell{-0.05**\\(0.02)}\\

@@

\hspace{1em}Women’s Log Annual Earnings & \specialcell{9.44\\(1.59)} & \specialcell{9.55\\(1.59)} & \specialcell{9.47\\(1.55)} & \specialcell{9.52\\(1.52)} & \specialcell{0.08**\\(0.02)} & \specialcell{-0.08*\\(0.05)}\\

@@

\item[1] Source: The 1970-1990 Census for synthetic parents, and 1994-2019 Current Population Surveys (CPS) for children's outcomes
\item[2] The data is restricted to native-born United States citizens between 1994 and 2019 who are also White and between the ages of 25 and 40, and who identify as Hispanic. I identify the ethnicity of a person's parents through the parent's place of birth. A parent is Hispanic if they were born in a Spanish-speaking country. A parent is White if they were born in the United States.

### 2023-04-16 my_paper/tables/tab05-regression.tex
some edits

\begin{table}[!h]

\caption{Effect of Having Hispanic Last Name \label{tab:lastnamereg}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcc}
\toprule
  & \specialcell{(1) \\ Log annual earnings} & \specialcell{(2) \\  Log annual earnings}\\
\midrule
$WH_{i}$ & \num{-0.14}*** & \num{-0.09}***\\
 & (\num{0.03}) & (\num{0.02})\\
$HW_{i}$ & \num{-0.20}*** & \num{-0.11}***\\
 & (\num{0.02}) & \vphantom{1} (\num{0.01})\\
$HH_{i}$ & \num{-0.24}*** & \num{-0.12}***\\
 & (\num{0.02}) & (\num{0.01})\\
\midrule
$HW_{i} - WH_{i}$ & -0.06** & -0.02\\
 & (0.03) & (0.02)\\
\midrule
Observations & \num{129359} & \num{129359}\\
State FE & X & X\\
Year FE & X & X\\
\textit{Controlling for:} &  & \\
Hours Worked & X & X\\
Age & X & X\\
Education &  & X\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] \footnotesize{This table includes the estimation results of equation (\ref{eq:1a}).}
\item[2] \footnotesize{The four groups stand for White Husband White Wife (WW), White Husband Hispanic Wife (WH), Hispanic Husband White (HW), and Hispanic Husband Hispanic Wife (HH).}
\item[3] \footnotesize{The sample is restricted to men working full-time full-year and are waged and salaried workers.}
\item[4] \footnotesize{Column one has the regression results when controlling for hours worked, age, and fixed effects. Column two has the results after controlling for education.}
\item[5] \footnotesize{Standard errors are clustered on the state level.}
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\begin{table}[H]

\caption{Effect of Having Hispanic Last Name \label{tab:lastnamereg}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcc}
\toprule
  & \specialcell{(1) \\ Log annual earnings} & \specialcell{(2) \\  Log annual earnings}\\
\midrule
$HW_{i}$ & \num{-0.05}** & \num{-0.02}\\
 & (\num{0.02}) & (\num{0.02})\\
\midrule
State FE & X & X\\
Year FE & X & X\\
\textit{Controlling for:} &  & \\
Hours Worked & X & X\\
Age & X & X\\
Education &  & X\\
Observations & \num{2423} & \num{2423}\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] \footnotesize{This table includes the estimation results of equation (\ref{eq:1a}).}
\item[2] \footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}
\item[3] \footnotesize{The sample is restricted to men working full-time full-year and are waged and salaried workers.}
\item[4] \footnotesize{Column one has the regression results when controlling for hours worked, age, and fixed effects. Column two has the results after controlling for education.}
\item[5] \footnotesize{Standard errors are clustered on the state level.}
\end{tablenotes}
\end{threeparttable}}
\end{table}

### 2023-04-16 output/tables/tab02-observations-by-couple.tex
some edits

\caption{Number of Children by Parental Type \label{tab:mat1}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{>{}lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Perental Type} \\
\cmidrule(l{3pt}r{3pt}){2-5}
  & \specialcell{White Father \\ White Mother} & \specialcell{White Father \\ Hispanic Mother} & \specialcell{Hispanic Father \\ White Mother} & \specialcell{Hispanic Father \\ Hispanic Mother}\\
\midrule
\textbf{\specialcell{Observations\\Share}} & \specialcell{3,828,024\\0.95} & \specialcell{24,306\\0.01} & \specialcell{35,841\\0.01} & \specialcell{135,300\\0.03}\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[1] Source: Current Population Surveys (CPS) 1994-2019
\item[2] The sample includes Whites, who are married, and are between the ages 25 and 40. Ethnicity of a person's parents are identified by the parent's place of birth. A parent is Hispanic if she/he was born in a Spanish-speaking country. A parent is White she/he was born in the United States.
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\caption{Couples' Type \label{tab:mat2}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{>{}lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Couples Type} \\
\cmidrule(l{3pt}r{3pt}){2-5}
  & \specialcell{White Husband \\ White Wife} & \specialcell{White Husband \\ Hispanic Wife} & \specialcell{Hispanic Husband \\ White Wife} & \specialcell{Hispanic Husband \\ Hispanic Wife}\\
\midrule
\textbf{\specialcell{Observations\\Share}} & \specialcell{1,286,731\\0.97} & \specialcell{7,178\\0.01} & \specialcell{7,606\\0.01} & \specialcell{20,911\\0.02}\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[1] Source: 1970-1990 Census
\item[2] The sample includes Whites, who are married, and are between the ages 25 and 40. Ethnicity of a person's parents are identified by the parent's place of birth. A parent is Hispanic if she/he was born in a Spanish-speaking country. A parent is White she/he was born in the United States.
\end{tablenotes}
\end{threeparttable}}
\end{table}

### 2023-04-16 output/tables/tab06-regression.tex
some edits

\begin{table}[!h]

\caption{Effect of Having Hispanic Last Name \label{tab:identreg}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcc}
\toprule
  & \specialcell{(1) \\ Log annual earnings} & \specialcell{(2) \\  Log annual earnings}\\
\midrule
$WH_{i} \times Hispanic_{i}$ & \num{-0.13}** & \num{-0.06}\\
 & (\num{0.05}) & \vphantom{1} (\num{0.05})\\
$HW_{i} \times Hispanic_{i}$ & \num{-0.16}*** & \num{-0.11}**\\
 & (\num{0.05}) & (\num{0.05})\\
$HH_{i} \times Hispanic_{i}$ & \num{-0.11}** & \num{-0.06}\\
 & (\num{0.05}) & (\num{0.04})\\
\midrule
$HW_{i} \times Hispanic_{i} - WH_{i} \times Hispanic_{i}$ & -0.03 & -0.04\\
 & (0.07) & (0.07)\\
\midrule
Observations & \num{129359} & \num{129359}\\
\textit{Controlling for:} &  & \\
Hours Worked & X & X\\
Age & X & X\\
Year FE & X & X\\
Education &  & X\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] \footnotesize{This table includes the estimation results of equation (\ref{eq:iden}).}
\item[2] \footnotesize{The four groups stand for White Husband White Wife (WW), White Husband Hispanic Wife (WH), Hispanic Husband White (HW), and Hispanic Husband Hispanic Wife (HH). $Hispanic_{i}$ is a dummy variable equal to one if a person identifies as Hispanic and zero otherwise.}
\item[3] \footnotesize{The sample is restricted to men working full-time full-year and are waged and salaried workers.}
\item[4] \footnotesize{Column one has the regression results when controlling for hours worked, age, and years of fixed effects. Column two has the results after controlling for education.}
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\begin{table}[H]

\caption{Effect of Having Hispanic Last Name \label{tab:identreg}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcc}
\toprule
  & \specialcell{(1) \\ Log annual earnings} & \specialcell{(2) \\  Log annual earnings}\\
\midrule
$HW_{i} \times Hispanic_{i}$ & \num{-0.02} & \num{-0.02}\\
 & (\num{0.08}) & (\num{0.07})\\
$Hispanic_{i}$ & \num{-0.11}** & \num{-0.06}\\
 & (\num{0.05}) & (\num{0.05})\\
$HW_{i}$ & \num{-0.03} & \num{0.00}\\
 & (\num{0.08}) & (\num{0.06})\\
\midrule
State FE & X & X\\
Year FE & X & X\\
\textit{Controlling for:} &  & \\
Hours Worked & X & X\\
Age & X & X\\
Education &  & X\\
Observations & \num{2423} & \num{2423}\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] \footnotesize{This table includes the estimation results of equation (\ref{eq:iden}).}
\item[2] \footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother, and Hispanic is an indicator variable that is equal to one if a person self-identifies as Hispanic.}
\item[3] \footnotesize{The sample is restricted to men working full-time full-year and are waged and salaried workers.}
\item[4] \footnotesize{Column one has the regression results when controlling for hours worked, age, and fixed effects. Column two has the results after controlling for education.}
\end{tablenotes}
\end{threeparttable}}
\end{table}
